%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}


\begin{center}
    {\Huge \scshape Rayen Ghali} \\ 
    \vspace{1pt}
    AI Research Assistant \textbar\ MASc Student \\ \vspace{1pt}
\end{center}

\vspace{-4.3\baselineskip} % Move up to align contact info with name
\begin{flushright}
    \raisebox{-0.2\height}{\faPhone\ +1 506-925-0056} \\
    \href{mailto:rayenghali02@gmail.com}{\raisebox{-0.2\height}{\faEnvelope\ \underline{rayenghali02@gmail.com}}} \\
    \href{https://linkedin.com/in/rayen-ghali-63718b1a5}{\raisebox{-0.2\height}{\faLinkedin\ \underline{rayen-ghali}}} \\
    \href{https://github.com/Rayen023}{\raisebox{-0.2\height}{\faGithub\ \underline{Rayen023}}} \\
\end{flushright}
\vspace{-1.8\baselineskip} % Adjust the space here
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
     \resumeSubheading
          {University of Moncton }
          {Jan. 2024 -- Dec. 2025}
          {Master of Applied Science (MASc)}
        {New Brunswick, Canada }
    \resumeSubheading
      {National Institute of Applied Science and Technology (INSAT)}
      {Sep. 2018 -- Oct 2023}
      {Engineering studies in Instrumentation and Industrial Maintenance (Graduated with High Honors) }
    {Tunis, Tunisia }

%    \resumeSubheading
%      {Pioneer High School of Sousse}
%      {Sep. 2014 -- 2018}
%      {Bachelor's degree in Mathematics (Graduated with Honors)}
%      {Sousse, Tunisia}
      
\resumeSubHeadingListEnd

    %\resumeSubHeadingListEnd
\vspace{-1.5\baselineskip} % Adjust the space here

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{CEAAC (Centre d'études acadiennes Anselme-Chiasson)}{Jun 2024 -- Nov 2024}
{AI Research Assistant}{New Brunswick, Canada}
\resumeItemListStart
\resumeItem{Implementing an open-access natural language processing system with agentic retrieval augmented generation for efficient querying of Acadian archives.}
\resumeItem{Developing a ChatGPT-like interface to enhance accessibility of Acadian heritage for researchers and the public, leveraging large language models and knowledge graphs.}
\resumeItem{Designing a knowledge management system to integrate expert archivists' insights into the AI-powered query process.}
\resumeItem{Project website: chatacadien.ca}
\resumeItem{Tech stack: Python, Langchain, Neo4j, Docker.}
\resumeItemListEnd
\resumeSubheading
{LARIHS Lab, University of Moncton}{Dec 2023 -- Present}
{AI Research Assistant}{New Brunswick, Canada}
\resumeItemListStart
\resumeItem{Collaborating on diverse projects, focusing on Robotics and AI research in computer vision for few-shot defect detection and Big Data Time Series Analysis.}
\resumeItem{Tech stack: Python, PyTorch, Pandas, Bash.}
\resumeItemListEnd


\resumeSubheading
{LARIHS Lab, University of Moncton}{May 2023 -- Aug 2023}
{AI Research Intern}{New Brunswick, Canada}
\resumeItemListStart
\resumeItem{End-of-studies Project focused on 'Industrial surface defect detection employing computer vision and a KUKA arm robot.' Funded by Mitacs Globalink scholarship.}
\resumeItem{Applying contrastive learning with YOLO and DETR based models for few-shot object detection for limited datasets of industrial surface defects for wood and steel products.}
\resumeItem{Explore techniques to improve object detection of small-size defects.}
\resumeItem{Tech stack: Python, PyTorch, Bash, SAHI}
\resumeItemListEnd

\resumeSubheading
{TICDCE (Tunis International Center for Digital Cultural Economy)}{Jul 2022 -- Sept 2022}
{Data Science Intern}{Hybrid}
\resumeItemListStart
\resumeItem{Create a recommendation system based on collaborative filtering for tourists interested in historical places in Tunisia.}
\resumeItem{Explore different models of recommendation systems (Content-Based, Collaborative, or Hybrid).}
\resumeItem{Apply Augmentation techniques for a private dataset containing numeric and categorical features.}
\resumeItem{Tech stack: Python, TensorFlow, scikit-learn, SMOTE.}
\resumeItemListEnd

\resumeSubheading
{STMicroelectronics | INSAT}{Feb 2022 - June 2022}
{Embedded Systems Developer Intern}{Tunis, Tunisia}
\resumeItemListStart
\resumeItem{Load image decoding library libsail on top of Azure RTOS libraries.}
\resumeItem{Contribute to the realization of a demo based on the ported libsail library running on an STM32 card.}
\resumeItem{Tech Stack: C/C++, libsail, STM32CubeIDE, Git.}
\resumeItemListEnd

\resumeSubheading
{ST2i (Société Tunisienne d'Informatique pour l'Ingénierie)}{Jul 2021 -- Sept 2021}
{Back-End Developer Intern}{Hybrid}
\resumeItemListStart
\resumeItem{Study and compare different open-source IAM (or IdP) layers based on OAuth 2.0 for identity management and user access control.}
\resumeItem{Implement the 'Keycloak' layer as a RESTful API in a micro-service architecture application.}
\resumeItem{Tech Stack: JAVA, Angular, Spring Boot, PostgreSQL.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-1\baselineskip} % Adjust the space here

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\noindent
\begin{minipage}[t]{0.49\textwidth}
    \textbf{Programming Languages}: Python, JAVA \\[4pt]
    \textbf{Databases}: MYSQL, MongoDB, PostgreSQL \\[4pt]
    \textbf{Version Control}: Git, Docker \\[4pt]
    \textbf{Deep Learning Frameworks}: Pytorch
\end{minipage}
\hfill
\begin{minipage}[t]{0.49\textwidth}
    \textbf{Data Science and Visualization Stack}:
    \begin{itemize}[itemsep=4pt, topsep=4pt, partopsep=0pt, parsep=0pt, left=0pt] % Adjust the itemsep parameter
        \item \textbf{Data Processing}: Pandas, Numpy, Scikit-Learn
        \item \textbf{Data Visualization}: Matplotlib, Seaborn, Plotly
        \item \textbf{Dashboards}: Streamlit
    \end{itemize}
\end{minipage}



 \vspace{0.8pt}

\section{Languages}
\begin{multicols}{3}
    \begin{itemize}[itemsep=0pt, parsep=0pt, left=0pt, label={}]
        \item\small\columnbreak \textbf{Arabic :} Native
        \item\small\columnbreak \textbf{French :} Bilingual
        \item\small\columnbreak \textbf{English :} Full Professional Proficiency
            \end{itemize}
\end{multicols}

 \vspace{-0.8pt}


\iffalse

%------RELEVANT COURSEWORK-------
\section{Certifications}
\begin{multicols}{4}
    \begin{itemize}[itemsep=0pt, parsep=0pt, left=0pt, label={}]
        \item\small\columnbreak \textbf{AI 900: Azure AI Fundamentals (Microsoft)}
            \item Implement "Best practices" to develop test sets as well as DL applications with TensorFlow.
        
        \item\small\columnbreak \textbf{Google IT Automation with Python Specialization (Google)}
            \item Use Git and GitHub
            \item Troubleshoot and debug complex issues
            \item Apply automation at scale
        
        \item\small\columnbreak \textbf{Structuring Machine Learning Projects (DeepLearning.AI)}
            \item Demonstrate fundamental knowledge of ML, AI and related Microsoft Azure services.
        
        \item\small\columnbreak \textbf{Developing AI Applications on Azure (Coursera)}
            \item Explore pre-trained ML models from Microsoft, and state-of-the-art solutions for computer vision and NLP
    \end{itemize}
\end{multicols}

\fi



\vspace{1pt}

%-----------INVOLVEMENT---------------
\section{Extracurricular Activities}
    \resumeItemListStart
        \resumeItem{Member, Aerobotix INSAT Club: Participated in various technical trainings and competitions, cultivating teamwork skills for collaborative projects.}
        \resumeItem{Webmaster, IEEE INSAT IAS Club (Industry Applications Society): Contributed to the planning and organization of the event IAS Annual Meeting 2021. Designed and managed the introductory event website.}
        \resumeItem{Kaggle Notebook expert: Actively participated in Kaggle competitions involving Natural Language Processing, Computer Vision, and Time Series. Kaggle profile at \href{https://www.kaggle.com/rayenghali023}{\raisebox{-0.2\height} {\faKaggle \underline{ rayenghali023}}} } \resumeItemListEnd




\vspace{1pt}
    
\end{document}
